Parametric analysis of ambisonic audio

### 2020-06-28 Chapters/CoherenceEstimation.tex
on work

\todo{In this chapter}, we study diffuseness estimation by subjecting a tetrahedral microphone array to spherically isotropic noise fields.
The motivation for this work is, first, that tetrahedral arrays are a well known type of microphone arrays, which have today become popular for applications related to Virtual and Augmented Reality. 
Second, the spherical isotropic sound field is known to be a good approximation to the reverberant part of the sound field in a room \cite{elko_spatial_2001, mccowan_microphone_2003}, and therefore it would be interesting to investigate how different microphone arrays behave under such conditions.

@@

\subsection{Simulation}
Spherical isotropic noise has been generated following the \textit{geometrical method} \cite{habets_generating_2007, habets_comments_2010}, using $I = 1024$ plane waves. The resulting \textit{A-Format} signals correspond to a virtual tetrahedral microphone array mimicking the Ambeo\footnote{Sennheiser Ambeo VR Mic. 
\todo{https://en-us.sennheiser.com/microphone-3d-audio-ambeo-vr-mic}}
characteristics ($R=0.015$ meter, $\alpha=0.5$). 
The generated audio has a duration of 60 seconds.

@@

\begin{figure}
	\includegraphics[width=\textwidth]{Figures/CoherenceEstimation/Figure1}
    \caption{\label{fig:Fig1}\textit{A-Format} coherence between microphone signals. Left: $\text{MSC}$ as a function of the frequency of theoretical, simulated and recorded \textit{((BLD,BRU)},  $N=5, I=64$) signals. Right: mean error $\bar{\varepsilon}$ of the recorded signals' $MSC$ \textit{(BLD,BRU)} compared to the simulated values, for all values of $N$ and $I$.\todo{REDO FIGURE WITH N AND I}}
\end{figure}

@@

\subsection{B-Format} 
\begin{figure}
	\includegraphics[width=\textwidth]{Figures/CoherenceEstimation/Figure2}
	\caption{\label{fig:Fig2} Estimated \textit{B-Format} coherence ($\Delta$) of a simulated diffuse sound field, as a function of the temporal averaging vicinity radius $r$. Left: $\Delta(k)$ for different values of $r$, with (coarse) and without (fine) application of radial filters. Right: mean and standard deviation of $\Delta(k)$ as a function of $r$.}
\end{figure}

@@

@@

As a remark, the comparison between Figs.~\ref{fig:Fig1} and \ref{fig:Fig2} provides evidence that the application of the spherical harmonic transform might be able to yield more accurate diffuseness estimations, due to a better signal conditioning \cite{epain_spherical_2016}.\\

\begin{figure}
	\includegraphics[width=\textwidth]{Figures/CoherenceEstimation/Figure3}
	\caption{\label{fig:Fig3}\textit{B-Format coherence} between microphone signals. Left: $\Delta$ of simulated and recorded ($N=5, I=64$) signals. Right: $\bar{\varepsilon}$ of the recorded signals coherence across all values of $N$ and $I$.\todo{REDO FIGURE} }
\end{figure}

>>>>

In this Chapter, we study diffuseness estimation by subjecting a tetrahedral microphone array to spherically isotropic noise fields.
The motivation for this work is, first, that tetrahedral arrays are a well known type of microphone arrays, which have today become popular for applications related to Virtual and Augmented Reality. 
Second, the spherical isotropic sound field is known to be a good approximation to the reverberant part of the sound field in a room \cite{elko_spatial_2001, mccowan_microphone_2003}, and therefore it would be interesting to investigate how different microphone arrays behave under such conditions.

@@

\subsection{Simulation}
Spherical isotropic noise has been generated following the \textit{geometrical method} \cite{habets_generating_2007, habets_comments_2010}, using $I = 1024$ plane waves. The resulting \textit{A-Format} signals correspond to a virtual tetrahedral microphone array mimicking the Ambeo\footnote{Sennheiser Ambeo VR Mic \cite{sennheiser}.}
characteristics ($R=0.015$ meter, $\alpha=0.5$). 
The generated audio has a duration of 60 seconds.

@@

@@

\begin{figure}[th]
	\includegraphics[width=\textwidth]{Figures/CoherenceEstimation/Untitled1}
    \caption{\label{fig:Fig1}\textit{A-Format} coherence between microphone signals. Left: $\text{MSC}$ as a function of the frequency of theoretical, simulated and recorded \textit{((BLD,BRU)},  $N=5, I=64$) signals. Right: mean error $\bar{\varepsilon}$ of the recorded signals' $MSC$ \textit{(BLD,BRU)} compared to the simulated values, for all values of $N$ and $I$.}
\end{figure}

\subsection{B-Format}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{Figures/CoherenceEstimation/Figure2}
	\caption{\label{fig:Fig2} Estimated \textit{B-Format} coherence ($\Delta$) of a simulated diffuse sound field, as a function of the temporal averaging vicinity radius $r$. Left: $\Delta(k)$ for different values of $r$, with (coarse) and without (fine) application of radial filters. Right: mean and standard deviation of $\Delta(k)$ as a function of $r$.}
\end{figure}

@@

As a remark, the comparison between Figs.~\ref{fig:Fig1} and \ref{fig:Fig2} provides evidence that the application of the spherical harmonic transform might be able to yield more accurate diffuseness estimations, due to a better signal conditioning \cite{epain2016spherical}.\\

\begin{figure}
	\includegraphics[width=\textwidth]{Figures/CoherenceEstimation/Untitled2}
	\caption{\label{fig:Fig3}\textit{B-Format coherence} between microphone signals. Left: $\Delta$ of simulated and recorded ($N=5, I=64$) signals. Right: $\bar{\varepsilon}$ of the recorded signals coherence across all values of $N$ and $I$.}
\end{figure}

### 2020-06-28 Chapters/ReververationTimeEstimation.tex
on work

The IRs are FOA room impulse responses simulated by the image method with the \textit{Multichannel Acoustic Signal Processing} library \todo{[ref to chapter?]}. There are 9 different IRs of 1 s, with random $T_{60}$ values in the range between 0.4 s and 1.1 s approximately, estimated by the $T_{10}$ method at the 1 kHz band. The angular position of the sources is randomized for each IR, while the receiver position is fixed at the room center, which has a size of $10.2 \times 7.1 \times 3.2$ m. The source distance is set to half the \textit{critical distance}, thus providing positive DRRs.

>>>>

The IRs are FOA room impulse responses simulated by the image method with the \textit{Multichannel Acoustic Signal Processing} library (Section~\ref{sec:masp}). There are 9 different IRs of 1 s, with random $T_{60}$ values in the range between 0.4 s and 1.1 s approximately, estimated by the $T_{10}$ method at the 1 kHz band. The angular position of the sources is randomized for each IR, while the receiver position is fixed at the room center, which has a size of $10.2 \times 7.1 \times 3.2$ m. The source distance is set to half the \textit{critical distance}, thus providing positive DRRs.

### 2020-06-28 Chapters/ScientificBackground.tex
on work

\subsection{Nomenclature}
\todo{is this name correct? }
Throughout the Thesis, we refer to time-domain signals with lowercase, e.g. $x(t)$, with $t$ as the time index.

@@

Furthermore, sound field reconstruction with Eq.~\ref{eq:decodingequation2} is only possible when the loudspeakers are evenly located on the 3D space; in other words, the speaker layout must take the form of one of the five \textit{Platonic solids}: tetrahedron, cube, octahedron, dodecahedron or icosahedron.
Provided that this condition is usually difficult to fulfil in real scenarios, there are several methods which allow ambisonic decoding for such \textit{irregular} layouts. One of the most commonly used is the AllRAD method \todo{cite zotter}. AllRAD proposes a two step decoding: first, the ambisonic signal is decoded to a nearly-uniform layout of virtual speakers. Then, the signals of the virtual speakers are further distributed into the real speakers by the \textit{Vector-Based Amplitude Panning (VBAP)} method \todo{cite pulkki}.

>>>>

\subsection{Nomenclature}

Throughout the Thesis, we refer to time-domain signals with lowercase, e.g. $x(t)$, with $t$ as the time index.

@@

Furthermore, sound field reconstruction with Eq.~\ref{eq:decodingequation2} is only possible when the loudspeakers are evenly located on the 3D space; in other words, the speaker layout must take the form of one of the five \textit{Platonic solids}: tetrahedron, cube, octahedron, dodecahedron or icosahedron.
Provided that this condition is usually difficult to fulfil in real scenarios, there are several methods which allow ambisonic decoding for such \textit{irregular} layouts. One of the most commonly used is the AllRAD method \cite{zotter2012all}. AllRAD proposes a two step decoding: first, the ambisonic signal is decoded to a nearly-uniform layout of virtual speakers. Then, the signals of the virtual speakers are further distributed into the real speakers by the \textit{Vector-Based Amplitude Panning (VBAP)} method \cite{pulkki1997virtual}.
